### 2021-10-02 docs/paper/sections/2_related_work.tex
Restructure paper: extract split up approach, merge implementation
Mention type analyis in related work

\subsection{Mining dependencies}
\label{sec:related_work/dependencies}

@@

\subsection{Mining usage information}
\label{sec:related_work/usage_information}

@@

However, the precision of ASTs is limited for dynamically typed languages such as JavaScript.
For this reason, a common data structure that can be used to improve type information are \emph{call graphs} that are either \emph{static} (i.e., the result of a theoretical analysis of the source code) or \emph{dynamic} (i.e., empirically recorded during program execution).
While the latter type has a higher potential for including a maximum of contextual information, the former has the advantage of being applicable to a larger probe of source code for that no concrete entry points are available.
There are many solutions that analyze the structure of programs and extract the relevant information to build call graphs:

>>>>

\subsection{Searching dependency graphs}
\label{sec:related_work/dependencies}

@@

\subsection{Extracting usage samples}
\label{sec:related_work/usage_samples}

@@

However, the precision of ASTs is limited for \emph{dynamically typed} languages such as JavaScript or Python.
As opposed to static typing, the value type of an expression in a dynamically typed language may be unknown at the compile time of the program.
For this reason, a \emph{type analysis} can be performed to predict the runtime types of all expressions in the AST \citep{jensen2009type}.
Usually, this is accomplished by analyzing the control flow of a program and inferring the possible types of every variable or function.
Another useful data structure for enhancing type information are \emph{call graphs} that are either gained \emph{statically} (i.e., the result of a theoretical analysis of the source code) or \emph{dynamically} (i.e., empirically recorded during program execution).
While the latter method has a higher potential for including a maximum of contextual information, the former has the advantage of being applicable to a larger probe of source code for that no concrete entry points are available.
Many solutions exist that analyze the structure of programs and extract relevant information to build call graphs:

### 2021-10-02 docs/paper/sections/5_usage_mining.tex
Refactor and fix figure and footnote positioning
Fix footnote positioning; use ACM colors
Mention type analyis in related work

\begin{figure*}
	\newcommand\lowlight[1]{\textcolor{gray}{#1}}
	\newcommand\highlight[1]{\textcolor{red}{#1}}
	\centering
	\begin{subfigure}[t]{.32\linewidth}
		\input{sections/5_usage_mining/patterns/CallExpression}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{.32\linewidth}
		\input{sections/5_usage_mining/patterns/PropertyAccessExpression}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{.32\linewidth}
		\input{sections/5_usage_mining/patterns/JsxOpeningElement}
	\end{subfigure}

	\caption{AST patterns for example JavaScript/TypeScript expressions.
		The \highlight{highlighted} node contains the link to the declaration of the referenced identifier.
	}
	\label{fig:usage_mining/patterns}
\end{figure*}
\input{sections/5_usage_mining/patterns/JsxOpeningElement.postfigure.tex}

@@

In a second step, a static type analysis is performed against each dependency ASF together with the target package's ASF.
The results of the type analysis are attached to the ASF so that every identifier is annotated with a type symbol that links to the declaration of the type for the identifier.
For instance, after this step, every variable node will contain a link to the assignment node of this variable, and every function call expression will contain a link to the definition of this function. \TODO{Give example?}
The operating principle of this type analysis depends on the kind of programming language; i.e., in statically typed languages, type symbols can usually be retrieved from the declaration of an identifier, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
\TODO{Elaborate on the topics type analysis and static/dynamic typing in related work/introduction.}

>>>>

\begin{figure*}
	\begin{minipage}{\linewidth}
		\newcommand\textlowlight[1]{\textcolor{gray}{#1}}
		\newcommand\texthighlight[1]{\textcolor{accent1}{#1}}
		\begin{center}
			\begin{subfigure}[t]{.32\linewidth}
				\input{sections/5_usage_mining/patterns/CallExpression}
			\end{subfigure}
			\hfill
			\begin{subfigure}[t]{.32\linewidth}
				\input{sections/5_usage_mining/patterns/PropertyAccessExpression}
			\end{subfigure}
			\hfill
			\begin{subfigure}[t]{.32\linewidth}
				\input{sections/5_usage_mining/patterns/JsxOpeningElement}
			\end{subfigure}

			\caption{AST patterns for example JavaScript/TypeScript expressions.
				The \texthighlight{highlighted} node contains the link to the declaration of the referenced identifier.
			}
			\label{fig:usage_mining/patterns}
		\end{center}
	\end{minipage}
\end{figure*}

@@

In a second step, a static type analysis is performed against each dependency ASF together with the target package's ASF.
The results of the type analysis are attached to the ASF so that every identifier is annotated with a type symbol that links to the declaration of the type for the identifier.
For instance, after this step, every variable node will contain a link to the assignment node of this variable, and every function call expression will contain a link to the definition of this function. \TODO{Give example?}
The operating principle of this type analysis depends on the kind of programming language; i.e., in statically typed languages, type symbols can usually be retrieved from the declaration of an identifier, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
